\normalfont{A statistical analysis on factors that contributed/slowed down the spread of COVID-19}

### 2020-10-23 Manuscript/Manuscript.tex
PUB

\section{R code}
\begin{lstlisting}
# Provinces
Dati_Covid <- data.frame(read_excel("Dati Covid_prov_FULL.xlsx"))

row.names(Dati_Covid)<- Dati_Covid[,2]

prov_full.pca<-prcomp(Dati_Covid[,5:11], center = TRUE,scale. = TRUE)

summary(prov_full.pca)

autoplot(prov_full.pca,loadings = TRUE,loadings.size= 4,
loadings.colour = 'blue',
loadings.label = TRUE, loadings.label.size = 4,
label=TRUE,label.vjust=1.5,
loadings.label.repel=T,label.repel=T)
+ggtitle('Totale') + theme_bw()
+ theme(plot.title = element_text(hjust = 0.5))

fviz_eig(prov_full.pca,barcolor = "red",
barfill = "red",geom = c("bar"),addlabels= TRUE )
+labs(title = "Variances - PCA",
x = "Principal Components", y = "% of variances")
+theme_bw()+theme(plot.title = element_text(hjust = 0.5))

fviz_pca_var(prov_full.pca,col.var = "contrib",
gradient.cols = c("red","orange","blue"),
repel = TRUE,col.circle = "black",arrowsize = 1,labelsize = 0.5,
jitter = list(what = "both", width = 1, height = 1) ) 
+theme_bw()+theme(plot.title = element_text(hjust = 0.5))

corrplot(cor(Dati_Covid[,5:11]))
palette = colorRampPalette(c("green", "blue", "red")) (20)
heatmap(x = cor(Dati_Covid[,5:11]), col = palette, 
symm = TRUE, margins = c(10, 10),
 main = 'Provinces',dist(Dati_Covid[,5:11],method = 'euclidean'))

# Regions
Dati_Covid_reg <- data.frame(read_excel("Dati Covid reg_FULL.xlsx"))

row.names(Dati_Covid_reg) <-Dati_Covid_reg[,1]

reg_full.pca<-prcomp(Dati_Covid_reg[,2:11], center = TRUE,scale. = TRUE)

autoplot(reg_full.pca,loadings = TRUE,
loadings.size= 4, loadings.colour = 'blue',
loadings.label = TRUE, loadings.label.size = 4,
label=FALSE,label.vjust=1.5,
loadings.label.repel=T,label.repel=T)
+ggtitle('Regions') +theme_bw()+
theme(plot.title = element_text(hjust = 0.5))

summary(reg_full.pca)

fviz_eig(reg_full.pca,barcolor = "red",
barfill = "red",geom = c("bar"),addlabels= TRUE )
+labs(title = "Variances - PCA",
x = "Principal Components", y = "% of variances")
+theme_bw()+theme(plot.title = element_text(hjust = 0.5))
fviz_pca_var(reg_full.pca,col.var = "contrib",
gradient.cols = c("red","orange","blue"),
repel = TRUE,col.circle = "black",arrowsize = 1,
labelsize = 0.5,jitter = list(what = "both", width = 1, height = 1) )
 +theme_bw()
+theme(plot.title = element_text(hjust = 0.5))

corrplot(cor(Dati_Covid_reg[,2:11]))
palette = colorRampPalette(c("green", "blue", "red")) (20)

heatmap(x = cor(Dati_Covid_reg[,2:11]),
 col = palette, symm = TRUE, margins = c(10, 10),
 main = 'Regions', dist(Dati_Covid_reg[,2:11],method = 'euclidean'))
dend.dat<-dist(Dati_Covid_reg[,2:11] )

#World
Covid_mond <- data.frame(
read_excel("Covid_mond.xlsx"))

row.names(Covid_mond) <-Covid_mond[,1]

world.pca<-prcomp(Covid_mond[,6:14], center = TRUE,scale. = TRUE)

fviz_pca_var(world.pca,col.var = "contrib",
gradient.cols = c("red","orange","blue"),
repel = TRUE,col.circle = "black",arrowsize = 1,
labelsize = 0.5,jitter = list(what = "both", width = 1, height = 1) ) 
+theme_bw()+theme(plot.title = element_text(hjust = 0.5)) 
fviz_eig(world.pca,barcolor = "red",
barfill = "red",geom = c("bar"),addlabels= TRUE )
+labs(title = "Variances - PCA",
x = "Principal Components", y = "% of variances")
+theme_bw()+theme(plot.title = element_text(hjust = 0.5))

autoplot(world.pca,loadings = TRUE,loadings.size= 4,
loadings.colour = 'blue',
loadings.label = TRUE,
loadings.label.size = 5,label=FALSE,label.vjust=1.5,
loadings.label.repel=T,label.repel=T)
+ggtitle('World')
+theme_bw()+
theme(plot.title = element_text(hjust = 0.5)) 
summary(world.pca)

corrplot(cor(Covid_mond[,6:14]))

palette = colorRampPalette(c("green", "blue", "red")) (20)

heatmap(x = cor(Covid_mond[,6:14]), 
col = palette, symm = TRUE, margins = c(10, 10),
main = 'World',dist(Covid_mond[,6:14],method = 'euclidean'))

\end{lstlisting}
%------------------------------------------------

>>>>

\section{R code}
\definecolor{light-gray}{gray}{0.95}
\lstset{ columns=fullflexible, basicstyle=\ttfamily, backgroundcolor=\color{light-gray},xleftmargin=0.5cm,frame=lr,framesep=8pt,framerule=0pt,frame=single,breaklines=true, postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}}
\lstinputlisting[language=R]{R_code_unsup.R}
%------------------------------------------------
